Project Notes - Solution Descriptions

### 2020-03-05 StateOfPractice/Peter-Notes/Peter-Notes-SolutionDescriptions.tex
added a few LBM solvers

@@

@@

@@

@@

@@

>>>>

	\item elbe \\
	\href{https://www.tuhh.de/alt/elbe/home.html}{https://www.tuhh.de/alt/elbe/home.html}\\
	Found using www.swmath.org \\
	elbe is a highly efficient academic flow solver for the simulation of non-linear three-dimensional flow problems, such as violent impact, tank sloshing or Tsunami propagation, and highly turbulent singlephase flows for drag resistance, aerodynamic noise control and fluid-structure interactions. elbe, the efficient lattice boltzmann environment, is accelerated with recent graphics hardware (graphics processing units, GPUs). Thanks to the very efficient numerical backend, three-dimensional simulations of complex flows are possible in or near real-time. elbe can be considered as a prototype for next-generation CFD tools that allow for a real-time analysis of complex flow fields and simulation-based design. Being developed since late 2010, the main development efforts currently take place at the Institute for Fluid Dynamics and Ship Theory (FDS) at Hamburg University of Technology (TUHH), with external partners and contributors at University of Rhode Island and TU Braunschweig.

	\item eLBM \\
	No direct source\\
	Found using www.swmath.org \\
	Direct simulation of pore-scale two-phase visco-capillary flow on large digital rock images using a phase-field lattice Boltzmann method on general-purpose graphics processing units.

@@

	\item LBM-EP \\
	No direct source\\
	Found using www.swmath.org \\	
	LBM-EP: lattice-Boltzmann method for fast cardiac electrophysiology simulation from 3D images. Current treatments of heart rhythm troubles require careful planning and guidance for optimal outcomes. Computational models of cardiac electrophysiology are being proposed for therapy planning but current approaches are either too simplified or too computationally intensive for patient-specific simulations in clinical practice. This paper presents a novel approach, LBM-EP, to solve any type of mono-domain cardiac electrophysiology models at near real-time that is especially tailored for patient-specific simulations. The domain is discretized on a Cartesian grid with a level-set representation of patient’s heart geometry, previously estimated from images automatically. The cell model is calculated node-wise, while the transmembrane potential is diffused using Lattice-Boltzmann method within the domain defined by the level-set. Experiments on synthetic cases, on a data set from CESC’10 and on one patient with myocardium scar showed that LBM-EP provides results comparable to an FEM implementation, while being 10 − 45 times faster. Fast, accurate, scalable and requiring no specific meshing, LBM-EP paves the way to efficient and detailed models of cardiac electrophysiology for therapy planning.

	\item lbmpy \\
	\href{https://pypi.org/project/lbmpy/}{https://pypi.org/project/lbmpy/}\\
	Found using www.swmath.org \\
	Run fast fluid simulations based on the lattice Boltzmann method in Python on CPUs and GPUs. lbmpy creates highly optimized LB compute kernels in C or CUDA, for a wide variety of different collision operators, including MRT, entropic, and cumulant schemes.

@@

	\item Ludwig
	\\
	\href{https://github.com/ludwig-cf/ludwig}{https://github.com/ludwig-cf/ludwig}\\
	Found using Google search.\\
	Ludwig is a parallel code for the simulation of complex fluids, which include mixtures, colloidal suspensions, gels, and liquid crystals. It takes its name from Ludwig Boltzmann, as it uses a lattice Boltzmann method as a basis for numerical solution of the Navier Stokes equations for hydrodynamics. It typically combines hydrodynamics with a coarse-grained order parameter (or order parameters) to represent the "complex" part in a free energy picture. The code is written in standard ANSI C, and uses the Message Passing Interface for distributed memory parallelism. Threaded parallelism is also available via a lightweight abstraction layer ("Target Data Parallel" or "TargetDP") which currently supports either OpenMP or CUDA (NVIDIA GPUs) from a single source.

@@

	\item Mechsys \\
	\href{http://mechsys.nongnu.org/}{http://mechsys.nongnu.org/}\\
	Found using www.swmath.org \\
	MechSys is a programming library for the implementation of simulation tools in mechanics. Its source code is mainly written in C++ with easier to use templates for further customization.

@@

	\item openLBMflow \\
	\href{https://github.com/wme7/openLBMflow}{https://github.com/wme7/openLBMflow}\\
	Found using www.swmath.org \\
	The openLBMflow is an fast fluid flow solver based on Lattice Boltzmann Method. Main future are 2D and 3D code, single and multiphase models, Output data in VTK format can be directly open in Paraview. Download Windows or Linux binary version now.

@@

	\item ParallelLbmCranfield \\
	\href{https://github.com/mate-szoke/ParallelLbmCranfield}{https://github.com/mate-szoke/ParallelLbmCranfield}\\
	Found using www.swmath.org \\
	This software is a two dimensional parallel Lattice Boltzmann Method solver implemented in CUDA and PGAS UPC

	\item PowerFLOW \\
	\href{https://www.3ds.com/products-services/simulia/products/powerflow/}{https://www.3ds.com/products-services/simulia/products/powerflow/}\\
	Found using www.swmath.org \\
	PowerFLOW: Through the usage of our unique, inherently transient Lattice Boltzmann-based physics, Exa’s PowerFLOW® CFD solution performs simulations that accurately predict real world conditions. Using the PowerFLOW suite, engineers evaluate product performance early in the design process prior to any prototype being built — when the impact of change is most significant for design and budgets. PowerFLOW imports fully complex model geometry and accurately and efficiently performs aerodynamic, aeroacoustic and thermal management simulations.

	\item ProLB \\
	\href{http://www.prolb-cfd.com/}{http://www.prolb-cfd.com/}
	\\
	Found using Google search.\\
	ProLB is an innovative Computational Fluid Dynamics (CFD) software solution. Based on the Lattice-Boltzmann method, its successfully-validated solver performs inherently transient simulations of highly complex flows with a competitive turnaround time. ProLB‘s accurate aerodynamic and aeroacoustic modeling allows engineers to make early design decisions that optimize and shorten the product development process.
